---
title: "Popular names"
subtitle: "Week 6 Activity"
author: "Pei Hsuan Tang and Shlok Manan Patel"
date: "Sun Oct 4"
output: 
  html_notebook:
    fig_height: 3
    fig_width: 5
---

# Set Up

```{r message=FALSE}
# load necessary packages
rm(list = ls())
library(tidyverse)
library(dcData)
library(mosaic)
library(esquisse)
```


```{r}
# Load the BabyNames data into RStudio environment (from dcData package)
data("BabyNames")

```

# Activity

**Goal**: By the end of the activity, each team will create a graph (like Figure A.1 on p 159) showing ups and downs in the popularity of the names at your table according to the U.S. social security registry.  


### Step 1

####Description

The US Social Security Administration provides yearly lists of names given to babies. These data combine the yearly lists.

'BabyNames' is the raw data from the SSA. The case is a year-name-sex, for example: Jane F 1922. The count is the number of children of that sex given that name in that year. Names assigned to fewer than five children of one sex in any year are not listed, presumably out of privacy concerns.

Available variable:
name - sex - count - year

```{r}
## Helpful to look at the data a few different ways (see Ch 9 for more).

```

### Step 2

[This should be done by hand on paper, nothing to show in the HTML doc]


### Step 3 

##### What variable(s) from the raw data table do not appear at all in the graph?

sex

##### What variable(s) in the graph are similar to corresponding variables in the raw data table, but might have been transformed in some way?

popularity 



### Step 4

##### Have cases been filtered out?



##### Have cases been grouped and summarized within groups in any way?



##### Have any new variables been introduced?  If so, what the relationship between the new variables and existing variables?





### Step 5



### Step 6

[This should be done by hand on paper, nothing to show in the HTML doc]



### Step 7

```{r}


```


### Graph It!

Here's the sample code provided by the book:

```
GlyphReadyForm %>%
  ggplot(aes(x = year, y = total, group = name)) + 
  geom_line(size = 1, alpha = 0.5, aes(color = name)) + 
  ylab("Popularity") + xlab("Year")
```



Note: if someone in your group has a name that hasn't been registered with the US Social Security Administration for a baby born in the United States, it's okay that the student's name may not appear on the plot.